--- 
title: "Notas de aulas de Estatística Econômica"
author: "Marcos Minoru Hasegawa"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: abntex2
link-citations: yes
description: "Trata-se do material usado nas aulas de Estatística Econômica e Introdução à Econometria SE305 do curso de Economia da Universidade Federal do Paranà."
---

```{r setup, include=FALSE}
library(formatR)
library(knitr)
library(ggplot2)
knitr::opts_chunk$set(
	echo = TRUE,
	error = FALSE,
	fig.height = 4,
	fig.width = 4,
	message = FALSE,
	warning = FALSE,
	cache = FALSE,
	tidy = TRUE,
	tidy.opts = list(width.cutoff = 50)
)
options(OutDec = ",")
```

# Licença {-}

Como está descrito no repositório, os poucos códigos originais desenvolvidos ao longo do texto estão sob a licença **GNU GPLv3** .

O texto e as artes gráficas elaboradas de forma original estão sob licença **Creative Commons BY-NC-SA 4.0**.

# Pré-requisitos

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introdução {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-capit.Rmd-->

# Revisão de Literatura

Aqui o estado da arte mundo afora.

<!--chapter:end:02-capit.Rmd-->

# Methods

We describe our methods in this chapter.

<!--chapter:end:03-capit.Rmd-->

# Aplicações

Some _significant_ applications are demonstrated in this chapter.

## Exemplo um

## Examplo dois

<!--chapter:end:04-capit.Rmd-->

# Considerações Finais

Terminado um excelente livro digital.

<!--chapter:end:05-capit.Rmd-->

`r if (knitr::is_html_output()) '
# Referências {-}
'`

<!--chapter:end:06-capit.Rmd-->

